
\documentclass[12pt,a4paper,final]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{grey}

\usepackage{url}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.80]{geometry}
% \setlength{\hintscolumnwidth}{3cm}.

\usepackage[scale=0.80]{geometry}
\setlength{\hintscolumnwidth}{3cm}

% personal data
\name{Andrew}{Durnev}
\title{Software engineer}
\address{}{Saint-Petersburg}{Russian Federation}
\email{almatinez101@yandex.ru}
\social[github]{OGthug-coder}


\begin{document}
\makecvtitle

\section{Experience}

\cventry{August~2021 -- Now}{Backend-engineer}{First Line Software}{Remote/Saint-Petersburg}{}{
\begin{itemize}
    \item Working on cloud-based medical practice management software (.NET Framework/Core, ASP.NET, SQL Server, Azure, Google Cloud Platform, Docker). I am working on a project migration from Microsoft Azure services to Google Cloud Platform services and from .NET Framework to .NET Core.
    \item I worked on a performance boost on a project from one of the Big Four accounting firms project.
\end{itemize}}

\cventry{May~2021 -- August~2021}{Backend-engineer}{ITRetail}{Remote/Saint-Petersburg}{}{
\begin{itemize}
    \item Developing modern Point of Sales for American groceries market.
\end{itemize}}

\section{Volunteering}
\cventry{May~2020 -- now}{Web developer/data analyst}{OVD-Info}{Remote/Moscow}{}{
  OVD-Info is an independent human rights media project.
  I'm participating in development of information collection and analysis system for OVD-Info using SQL, Python and Django.
}

\section{Education}
\cvitem{2018--2022}{
  \textbf{Peter the Great St. Petersburg Polytechnic University}; \newline
  Institute of Applied Mathematics and Mechanics; \newline
  Mechanics and Mathematical modeling; \newline
}

\section{Languages}
\cvitemwithcomment{Russian}{Native speaker}{}
\cvitemwithcomment{English}{Fluent}{}

\section{Skills}
\subsection{Main:}
\cvitem{}{.NET (ASP.NET, Entity Framework), JavaScript (React) Python (Django, Flask), Git, Linux, CI/CD, Docker, RDBMS (PostgreSQL, SQL Server). }
\subsection{Experience with:}
\cvitem{}{Nginx, Azure, AWS, GCP, Kubernetes, Bash, \LaTeX, Matlab. }

\end{document}
